---
title: "Reproducible Pitch For my App"
author: "Noble Prince"
date: "11/5/2020 (MM/DD/YYYY)"
output:
  
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

The following presentation and the shiny app is part of the coursera project under the course developing data products.
This presentation is a reproducible pitch for the shiny app created which you can check the files for in the repository. This app is a simple distribution plotter app using random numbers and user input characteristics.

## Shiny Package and It's use

Shiny is a Web Application Framework for R. It is an incredibly easy to use package to build interactive and real time web apps with R.
For more details refer: http://127.0.0.1:16275/help/library/shiny/help/shiny-options
And for useful tips and tutorials on it refer: http://shiny.rstudio.com/tutorial/

Coming to the app for plotting distributions, it is a user friendly app incorporates submit button for easy understanding and produces plots with the help of user input values.

## My App

My app uses general tools of shiny package to produce an useful and interactive plot
Check out the following R snippet for the UI part
```{r, echo=TRUE, eval=FALSE}
library(shiny)
shinyUI(fluidPage(titlePanel("Distribution Plots using Random Numbers"),
sidebarLayout( sidebarPanel(selectInput("Distribution", "Select the Type of Distribution",
                        choices = c("Exponential","Normal")),
sliderInput("Number of Variables","Pick the sample size number to plot the values",
            100,3000,value = 500,step = 100),
conditionalPanel(condition = "input.Distribution == 'Normal'",
                textInput("Mean", "Select the mean", 5),
                textInput("Standard Deviation", "Select the SD",2)),
conditionalPanel(condition = "input.Distribution == 'Exponential'",
                textInput("lambda", "Select Exponential Lambda", 1)),
h5("Please press on 'Submit button' every time you change the input values"),
submitButton("Plot")),
        mainPanel(
            plotOutput("thePlot")))))
```

## My App contd..
This slide contains the snippet for server part. Both are simple and self explanatory if you know little basics of html and shiny package.
```{r, echo=TRUE, eval=FALSE}
library(shiny)
shinyServer(function(input, output) {
  output$thePlot <- renderPlot({
      distType <- input$Distribution
      size <- input$`Number of Variables`
      if(distType == "Normal"){
        Vector <- rnorm(size, mean = as.numeric(input$Mean),sd = as.numeric(input$`Standard Deviation`))
        }
      if(distType == "Exponential"){
        Vector <- rexp(size, rate = 1/as.numeric(input$lambda))}
      hist(Vector, col = "green")})})
```




